Notes on Validated Model Counting \\ Version of \today

### 2022-07-16 doc/mc-notes.tex
Start switch to k-argument And

\begin{table}
  \caption{CRAT Step Types.  $C$: clause identifier, $L$: literal, $V$: variable}
  \label{tab:crat:syntax}
\centering{
  \begin{tabular}{lllll}
    \multicolumn{4}{c}{Rule} & \multicolumn{1}{c}{Description} \\
    \midrule
    \makebox[5mm][l]{$C$} & \makebox[10mm][l]{\tt i}  & \makebox[15mm][l]{$L^{*}$ {\tt 0}} & \makebox[15mm][l]{}  & \makebox[20mm][l]{Input clause} \\
    $C$ & {\tt a} & $L^{*}$ {\tt 0} & $C^{+}$  {\tt 0} & Add RUP clause.  Explicit hint \\
    $C$ & {\tt a} & $L^{*}$ {\tt 0} &  {\tt * 0} & Add RUP clause.  Inferred hint \\
     & {\tt dc} & $C$             & $C^{+}$  {\tt 0} & Delete RUP clause.  Explicit hint \\
     & {\tt dc} & $C$             & {\tt * 0} & Delete RUP clause.  Inferred hint \\
    \midrule
    $C$    & {\tt p} & $V \; L \; L$    &                  & Declare $\pand$ operation \\
    $C$    & {\tt s} & $V \; L \; L$    & $C^{+}$ {\tt 0}  & Declare $\por$ operation.  Explicit hint \\ 
    $C$    & {\tt s} & $V \; L \; L$    & {\tt * 0}  & Declare $\por$ operation.  Inferred hint \\ 
%%        & {\tt ite} & $V \; L \; L\; L$    &                  & Declare $\pite$ operation \\
     & {\tt do} & $V$             &  & Delete operation. \\

@@

The declaration of a $\pand$ operation has the form:
\begin{center}
\begin{tabular}{ccccc}
  \makebox[5mm]{$i$} & \makebox[5mm]{{\tt p}} & \makebox[5mm]{$v$} & \makebox[5mm]{$l_1$} & \makebox[5mm]{$l_2$} \\
\end{tabular}
\end{center}
where $i$ is a new clause ID, $v$ is a positive integer that does not
correspond to any previous variable, and $l_1$ and $l_2$ are signed
integers representing literals of existing variables.
This declaration implicitly causes three clauses to be added to the proof:
\begin{center}
\begin{tabular}{cccc}
\makebox[10mm]{ID} & \multicolumn{3}{c}{Clause} \\
  $i$ & $v$ & $-l_1$ & $-l_2$ \\
  $i\!+\!1$ & $-v$ & $l_1$ & \\
  $i\!+\!2$ & $-v$ & $l_2$ & \\
\end{tabular}
\end{center}
The dependency sets for the arguments represented by literals $l_1$ and $l_2$ must be disjoint.

@@

\begin{figure}
  A).  CRAT File Contents
  \begin{center}
  \begin{tabular}{lcllll}
    \multicolumn{4}{c}{File line} & & \multicolumn{1}{c}{Explanation} \\
\midrule
    \makebox[5mm][l]{\tt 1} & \makebox[7mm]{\tt i}   & \makebox[20mm][l]{\tt 1 2 3 0}   &  \makebox[30mm]{}          & \makebox[5mm]{} & \makebox[40mm][l]{Input clause}\\
    {\tt 2}        & {\tt p}   & {\tt 4 -2 3}  &            & & Declare $p_4 = \obar{x}_2 \pand x_3$ \\
    {\tt 5}        & {\tt s}   & {\tt 5 2 4}   & {\tt 3 0}  & & Declare $s_5 = x_2 \por p_4$ \\
    {\tt 8}        & {\tt p}   & {\tt 6 -1 5}  &            & & Declare $p_6 = \obar{x}_1 \pand s_5$ \\
    {\tt 11}         & {\tt s}   & {\tt 7 1 6}   & {\tt 9 0}  & & Declare $s_7 = x_1 \por p_6$ \\
    {\tt 14} & {\tt a}  & {\tt 7 0} & {\tt 13 12 8 7 6 2 1 0} & & Assert unit clause $[s_7]$ \\
             & {\tt dc}  & {\tt 1}  & {\tt 4 5 10 11 14 0} & & Delete input clause \\
  \end{tabular}
  \end{center}
B). Proof Clauses
    \begin{center}
  \begin{tabular}{lcllll}
    \multicolumn{4}{c}{Clause} & & \multicolumn{1}{c}{Explanation} \\
\midrule
    \makebox[5mm][l]{\tt 1} & \makebox[7mm]{}   & \makebox[20mm][l]{\tt 1 2 3 0}   &  \makebox[30mm]{}          & \makebox[5mm]{} & \makebox[40mm][l]{Input clause}\\
    {\tt 2} &     & {\tt 4  2 -3 0}  &     & & Defining clauses for $p_4$ \\ 
    {\tt 3} &     & {\tt -4 -2 0}    & & & \\ %%Defining clause for $p_4$ \\ 
    {\tt 4} &     & {\tt -4 3 0}    &  & & \\ %%Defining clause for $p_4$ \\ 
            &     & {\tt -2 -4 0}   & {\tt 3 0}  & &  Mutual exclusion proof for $s_5$ \\
    {\tt 5} &     & {\tt -5 2 4 0}  &     & & Defining clauses for $s_5$ \\ 
    {\tt 6} &     & {\tt  5 -2 0}    &  &  \\  %%Defining clause for $s_5$ \\ 
    {\tt 7} &     & {\tt  5 -4 0}    &  & &  \\  %%Defining clause for $s_5$ \\ 
    {\tt 8} &     & {\tt 6  1 -5 0}  &    & & Defining clauses for $p_6$ \\ 
    {\tt 9} &     & {\tt -6 -1 0}    &  & &  \\  %%Defining clause for $p_6$ \\ 
    {\tt 10} &     & {\tt -6 5 0}    &  & &  \\  %%Defining clause for $p_6$ \\ 
            &     & {\tt -1 -6 0}   & {\tt 9 0}  & &  Mutual exclusion proof for $s_7$ \\
    {\tt 11} &     & {\tt -7 1 6 0}  &  & & Defining clauses for $s_7$ \\ 
    {\tt 12} &     & {\tt  7 -1 0}     & &  \\  %%Defining clause for $s_7$ \\ 
    {\tt 13} &     & {\tt  7 -6 0}     & &  \\  %%Defining clause for $s_7$ \\ 
    {\tt 14} &     & {\tt 7 0} & {\tt 13 12 7 6 2 1 0} & & Assert unit clause $[s_7]$ \\
             & {\tt dc}  & {\tt 1}  & {\tt 4 5 10 11 14 0} & & Delete input clause \\
  \end{tabular}
  \end{center}
  \caption{CRAT file \#1 for formula $x_1 \lor x_2 \lor x_3$, and the resulting set of proof clauses}
  \label{fig:c3:crat}
\end{figure}

@@

    \makebox[5mm][l]{\tt 1} & \makebox[7mm]{\tt i}   & \makebox[20mm][l]{\tt 1 2 3 0}   &  \makebox[30mm]{}          & \makebox[5mm]{} & \makebox[40mm][l]{Input clause $C_1$}\\
    {\tt 2} & {\tt i}   & {\tt -1 2 0}  &            & & Input clause $C_2$ \\
    {\tt 3} & {\tt p}   & {\tt 4 -2 -3}  &            & & Declare $p_4 = \obar{x}_2 \pand \obar{x}_3$ \\
    {\tt 6} & {\tt p}   & {\tt 5 -1 4}  &             & & Declare $p_5 = \obar{x}_1 \pand p_4 = \obar{x}_1 \pand \obar{x}_2 \pand \obar{x}_3$ \\
    {\tt 9} & {\tt a}  & {\tt -5 0} & {\tt 7 8 5 4 1 0} & & Assert $t_1 = \obar{p}_5 = x_1 \lor x_2 \lor x_3$ \\
            & {\tt dc}  & {\tt 1 } & {\tt 3 6 9 0} & & Delete clause $C_1$\\
    {\tt 10} & {\tt p}   & {\tt 6 1 -2} &              & & Declare $p_6 = x_1 \pand \obar{x}_2$ \\    
    {\tt 13} & {\tt a} & {\tt -6 0} & {\tt 12 11 2 0}  & & Assert $t_2 = \obar{p}_6 = \obar{x}_1 \lor x_2$ \\
            & {\tt dc}  & {\tt 2 } & {\tt 10 13 0} & & Delete clause $C_2$\\
    {\tt 14} & {\tt s}   & {\tt 7 5 6}   & {\tt 7 11 0}  & & Declare $s_7 = \obar{t}_1 \por \obar{t}_2$ \\
    {\tt 17} & {\tt a}  & {\tt -7 0}       & {\tt 9 13 14 0} & & Assert $t_3 = \obar{s}_7 = t_1 \land t_2$ \\
             & {\tt dc}  & {\tt 9}          & {\tt 15 17 0} & & Delete $t_1$\\
             & {\tt dc}  & {\tt 13}         & {\tt 16 17 0} & & Delete $t_2$\\
  \end{tabular}
  \end{center}  
B). Proof Clauses
  \begin{center}
  \begin{tabular}{lcllll}
    \multicolumn{4}{c}{Clause} & & \multicolumn{1}{c}{Explanation} \\
\midrule
    \makebox[5mm][l]{\tt 1} & \makebox[7mm]{}   & \makebox[20mm][l]{\tt 1 2 3 0}   &  \makebox[30mm]{}          & \makebox[5mm]{} & \makebox[40mm][l]{Input clause $C_1$}\\
    {\tt 2} &    & {\tt -1 2 0}  &            & & Input clause $C_2$ \\
    {\tt 3} &   & {\tt 4 2 3 0} &     & & Defining clauses for $p_4$ \\
    {\tt 4} &   & {\tt -4 -2 0} &     & & \\
    {\tt 5} &   & {\tt -4 -3 0} &     & & \\

    {\tt 6} &   & {\tt 5 1 -4 0} &    & & Defining clauses for $p_5$ \\
    {\tt 7} &   & {\tt -5 -1 0} &     & & \\
    {\tt 8} &   & {\tt -5 4 0} &      & & \\

    {\tt 9} &   & {\tt -5 0} & {\tt 7 8 5 4 1 0} & & Assert $t_1 = \obar{p}_5 = x_1 \lor x_2 \lor x_3$ \\
            & {\tt dc}  & {\tt 1 } & {\tt 3 6 9 0} & & Delete clause $C_1$\\

>>>>

\begin{table}
  \caption{CRAT Step Types.  $C$: clause identifier, $L$: literal, $V$: variable}
  \label{tab:crat:syntax}
\centering{
  \begin{tabular}{lllll}
    \multicolumn{4}{c}{Rule} & \multicolumn{1}{c}{Description} \\
    \midrule
    \makebox[5mm][l]{$C$} & \makebox[10mm][l]{\tt i}  & \makebox[15mm][l]{$L^{*}$ {\tt 0}} & \makebox[15mm][l]{}  & \makebox[20mm][l]{Input clause} \\
    $C$ & {\tt a} & $L^{*}$ {\tt 0} & $C^{+}$  {\tt 0} & Add RUP clause.  Explicit hint \\
    $C$ & {\tt a} & $L^{*}$ {\tt 0} &  {\tt * 0} & Add RUP clause.  Inferred hint \\
     & {\tt dc} & $C$             & $C^{+}$  {\tt 0} & Delete RUP clause.  Explicit hint \\
     & {\tt dc} & $C$             & {\tt * 0} & Delete RUP clause.  Inferred hint \\
    \midrule
    $C$    & {\tt p} & $V \; L^{2+}$ {\tt 0}    &                  & Declare $\pand$ operation \\
    $C$    & {\tt s} & $V \; L \; L$    & $C^{+}$ {\tt 0}  & Declare $\por$ operation.  Explicit hint \\ 
    $C$    & {\tt s} & $V \; L \; L$    & {\tt * 0}  & Declare $\por$ operation.  Inferred hint \\ 
%%        & {\tt ite} & $V \; L \; L\; L$    &                  & Declare $\pite$ operation \\
     & {\tt do} & $V$             &  & Delete operation. \\

@@

The declaration of a $\pand$ operation has the form:
\begin{center}
\begin{tabular}{ccccccccc}
  \makebox[5mm]{$i$} & \makebox[5mm]{{\tt p}} & \makebox[5mm]{$v$} & \makebox[5mm]{$l_1$} & \makebox[5mm]{$l_2$} &
  \makebox[5mm]{$\cdots$} & \makebox[5mm]{$l_k$} & \makebox[5mm]{\tt 0} \\
\end{tabular}
\end{center}
where $i$ is a new clause ID, $v$ is a positive integer that does not
correspond to any previous variable, and $l_1, l_2, \ldots, l_k$ is a sequence of $k$  ($k \geq 2$)
integers representing literals of existing variables.  
This declaration implicitly causes $k+1$ clauses to be added to the proof:
\begin{center}
\begin{tabular}{cccccc}
\makebox[10mm]{ID} & \multicolumn{5}{c}{Clause} \\
  $i$ & $v$ & $-l_1$ & $-l_2$ & $\cdots$ & $-l_k$\\
  $i\!+\!1$ & $-v$ & $l_1$  \\
  $i\!+\!2$ & $-v$ & $l_2$  \\
  & $\ldots$ \\
  $i\!+\!k$ & $-v$ & $l_k$  \\
\end{tabular}
\end{center}
The dependency sets for the arguments represented each pair of literals $l_{j_1}$ and $l_{j_2}$, for $1 \leq j_1 < j_2 \leq k$, must be disjoint.

@@

\begin{figure}
  A).  CRAT File Contents
  \begin{center}
  \begin{tabular}{lcllll}
    \multicolumn{4}{c}{File line} & & \multicolumn{1}{c}{Explanation} \\
\midrule
    \makebox[5mm][l]{\tt 1} & \makebox[7mm]{\tt i}   & \makebox[20mm][l]{\tt 1 2 3 0}   &  \makebox[30mm]{}          & \makebox[5mm]{} & \makebox[40mm][l]{Input clause}\\
    {\tt 2}        & {\tt p}   & {\tt 4 -2 3 0}  &            & & Declare $p_4 = \obar{x}_2 \pand x_3$ \\
    {\tt 5}        & {\tt s}   & {\tt 5 2 4}   & {\tt 3 0}  & & Declare $s_5 = x_2 \por p_4$ \\
    {\tt 8}        & {\tt p}   & {\tt 6 -1 5 0}  &            & & Declare $p_6 = \obar{x}_1 \pand s_5$ \\
    {\tt 11}         & {\tt s}   & {\tt 7 1 6}   & {\tt 9 0}  & & Declare $s_7 = x_1 \por p_6$ \\
    {\tt 14} & {\tt a}  & {\tt 7 0} & {\tt 13 12 8 7 6 2 1 0} & & Assert unit clause $[s_7]$ \\
             & {\tt dc}  & {\tt 1}  & {\tt 4 5 10 11 14 0} & & Delete input clause \\
  \end{tabular}
  \end{center}
B). Proof Clauses
    \begin{center}
  \begin{tabular}{lcllll}
    \multicolumn{4}{c}{Clause} & & \multicolumn{1}{c}{Explanation} \\
\midrule
    \makebox[5mm][l]{\tt 1} & \makebox[7mm]{}   & \makebox[20mm][l]{\tt 1 2 3 0}   &  \makebox[30mm]{}          & \makebox[5mm]{} & \makebox[40mm][l]{Input clause}\\
    {\tt 2} &     & {\tt 4  2 -3 0}  &     & & Defining clauses for $p_4$ \\ 
    {\tt 3} &     & {\tt -4 -2 0}    & & & \\ %%Defining clause for $p_4$ \\ 
    {\tt 4} &     & {\tt -4 3 0}    &  & & \\ %%Defining clause for $p_4$ \\ 
            &     & {\tt -2 -4 0}   & {\tt 3 0}  & &  Mutual exclusion proof for $s_5$ \\
    {\tt 5} &     & {\tt -5 2 4 0}  &     & & Defining clauses for $s_5$ \\ 
    {\tt 6} &     & {\tt  5 -2 0}    &  &  \\  %%Defining clause for $s_5$ \\ 
    {\tt 7} &     & {\tt  5 -4 0}    &  & &  \\  %%Defining clause for $s_5$ \\ 
    {\tt 8} &     & {\tt 6  1 -5 0}  &    & & Defining clauses for $p_6$ \\ 
    {\tt 9} &     & {\tt -6 -1 0}    &  & &  \\  %%Defining clause for $p_6$ \\ 
    {\tt 10} &     & {\tt -6 5 0}    &  & &  \\  %%Defining clause for $p_6$ \\ 
            &     & {\tt -1 -6 0}   & {\tt 9 0}  & &  Mutual exclusion proof for $s_7$ \\
    {\tt 11} &     & {\tt -7 1 6 0}  &  & & Defining clauses for $s_7$ \\ 
    {\tt 12} &     & {\tt  7 -1 0}     & &  \\  %%Defining clause for $s_7$ \\ 
    {\tt 13} &     & {\tt  7 -6 0}     & &  \\  %%Defining clause for $s_7$ \\ 
    {\tt 14} &     & {\tt 7 0} & {\tt 13 12 7 6 2 1 0} & & Assert unit clause $[s_7]$ \\
             & {\tt dc}  & {\tt 1}  & {\tt 4 5 10 11 14 0} & & Delete input clause \\
  \end{tabular}
  \end{center}
  \caption{CRAT file \#1 for formula $x_1 \lor x_2 \lor x_3$, and the resulting set of proof clauses}
  \label{fig:c3:crat}
\end{figure}

@@

    \makebox[5mm][l]{\tt 1} & \makebox[7mm]{\tt i}   & \makebox[20mm][l]{\tt 1 2 3 0}   &  \makebox[30mm]{}          & \makebox[5mm]{} & \makebox[40mm][l]{Input clause $C_1$}\\
    {\tt 2} & {\tt i}   & {\tt -1 2 0}  &            & & Input clause $C_2$ \\
    {\tt 3} & {\tt p}   & {\tt 4 -1 -2 -3 0}  &            & & Declare $p_4 = \obar{x}_1 \pand \obar{x}_2 \pand \obar{x}_3$ \\
    {\tt 7} & {\tt a}  & {\tt -4 0} & {\tt 7 8 5 4 1 0} & & Assert $t_1 = \obar{p}_4 = x_1 \lor x_2 \lor x_3$ \\
            & {\tt dc}  & {\tt 1 } & {\tt 3 6 9 0} & & Delete clause $C_1$\\
    {\tt 8} & {\tt p}   & {\tt 5 1 -2} &              & & Declare $p_5 = x_1 \pand \obar{x}_2$ \\    
    {\tt 11} & {\tt a} & {\tt -5 0} & {\tt 12 11 2 0}  & & Assert $t_2 = \obar{p}_5 = \obar{x}_1 \lor x_2$ \\
            & {\tt dc}  & {\tt 2 } & {\tt 10 13 0} & & Delete clause $C_2$\\
    {\tt 12} & {\tt s}   & {\tt 6 4 5}   & {\tt 7 11 0}  & & Declare $s_6 = \obar{t}_1 \por \obar{t}_2$ \\
    {\tt 15} & {\tt a}  & {\tt -6 0}       & {\tt 9 13 14 0} & & Assert $t_3 = \obar{s}_7 = t_1 \land t_2$ \\
             & {\tt dc}  & {\tt 7}          & {\tt 15 17 0} & & Delete $t_1$\\
             & {\tt dc}  & {\tt 11}         & {\tt 16 17 0} & & Delete $t_2$\\
  \end{tabular}
  \end{center}  
B). Proof Clauses
  \begin{center}
  \begin{tabular}{lcllll}
    \multicolumn{4}{c}{Clause} & & \multicolumn{1}{c}{Explanation} \\
\midrule
    \makebox[5mm][l]{\tt 1} & \makebox[7mm]{}   & \makebox[20mm][l]{\tt 1 2 3 0}   &  \makebox[30mm]{}          & \makebox[5mm]{} & \makebox[40mm][l]{Input clause $C_1$}\\
    {\tt 2} &    & {\tt -1 2 0}  &            & & Input clause $C_2$ \\
    {\tt 3} &   & {\tt 4 1 2 3 0} &     & & Defining clauses for $p_4$ \\
    {\tt 4} &   & {\tt -4 -1 0} &     & & \\
    {\tt 5} &   & {\tt -4 -2 0} &     & & \\
    {\tt 6} &   & {\tt -4 -3 0} &     & & \\
    {\tt 7} &   & {\tt -4 0} & {\tt 6 5 4 1 0} & & Assert $t_1 = \obar{p}_4 = x_1 \lor x_2 \lor x_3$ \\
            & {\tt dc}  & {\tt 1 } & {\tt 3 7 0} & & Delete clause $C_1$\\
